Meta-analysis

### 2019-10-31 05_MetaAnalysis.Rmd
log the pvalue for plotting

ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_pval))+
   geom_raster(aes(fill = lm_pval), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_abline(intercept = 0, slope = 1, colour = "red")+
   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu", direction = -1)

>>>>

ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval)))+
   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_abline(intercept = 0, slope = 1, colour = "red")+
   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu", direction = -1)
